---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggSpider

<!-- badges: start -->

<!-- badges: end -->

Geochemistry a branch of geology) uses a certain type of plots known as
"multi-elements normalized diagrams", or for short, "spider diagrams"
(or spidergrams, or spiderplots). They allow to display simultaneously
the composition of a rock for a group of elements, for instance for all
the Rare Earth Elements (REE) (i.e. La to Yb, atomic number 57 to 71).
There are a few additional conventional embellishments that I'm not
going to justify further (you can read about them ... ), but are
expected by the users.

Before I go further - yes, I'm aware of the conceptual issues with
parallel coordinates plots and I absolutely know what is problematic
with thse diagrams, but they are the convention in the subfield, so ours
is not to reason why, but to do or to die, etc.

A recipe for a plain spidergram: 1) Take the analysis for one or several
samples; 2) Select the elements of interest; 3) Normalize each analysis,
by dividing each element's composition by the concentration in a
reference material for this element 4) Arrange the elements in the
appropriate order 5) For each sample, - plot each element as a dot at
the right Y value - ... generally, using a log scale - ... generally,
connect the dots

## Installation

You can install the development version of ggSpider from
[GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jfmoyen/ggSpider")
```

## Example

See more in demo.R

```{r example}
library(tidyverse)
library(ggSpider)

data("atacazo")
ggspiderplot(atacazo,norm="Nakamura")+geom_line_continuous(aes(colour = SiO2))

```
